D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-05-12 doc/article/article.tex
Device

% 
% Graph Diagram
%
\section{Graph Diagram Recognition}

\subsection{Internal Representation}
In order to pass data through the components of the pipeline in a unified way, it was necessary to decide upon an internal representation of the graph diagram. It consists of \textbf{elements} and \textbf{relations}. The latter are linked to at least one element. Every element has a \textit{category} and possibly some \textit{inner} and \textit{outer text}. Every relation has a \textit{category} too, either a \textit{source} or \textit{target element} or both, and possibly \textit{text} related to it.

@@

\begin{table}[htbp]
\caption{Text Distance Metrics}
\centering
\begin{tabular}{lccc}
\hline
\textbf{Model} & \textbf{Hamming} & \textbf{Cosine} & \textbf{Euclidean} \\
\hline
microsoft-trocr-small-printed & 1.392 & 0.150 & 7133 \\
% microsoft-trocr-base-printed & 1.286 & 0.081 & 3594 \\
microsoft-trocr-small-handwritten & 1.346 & 0.100  & 3947 \\
microsoft-trocr-base-handwritten & 1.549 & 0.057 & 3003 \\
\hline
\end{tabular}
\label{tab:text_digitization}
\end{table}

Some examples of the different models applied to our graph diagram dataset can be seen in Figure~\ref{fig:text_digitization_results_1} and in Figure~\ref{fig:text_digitization_results_2}.

>>>>

% 
% Flowchart Diagram
%
\section{Flowchart Diagram Recognition}

\subsection{Internal Representation}
In order to pass data through the components of the pipeline in a unified way, it was necessary to decide upon an internal representation of the flowchart diagram. It consists of \textbf{elements} and \textbf{relations}. The latter are linked to at least one element. Every element has a \textit{category} and possibly some \textit{inner} and \textit{outer text}. Every relation has a \textit{category} too, either a \textit{source} or \textit{target element} or both, and possibly \textit{text} related to it.

@@

\begin{table}[htbp]
\caption{Text Distance Metrics}
\centering
\begin{tabular}{lccc}
\hline
\textbf{Model} & \textbf{Hamming} & \textbf{Cosine} & \textbf{Euclidean} \\
\hline
microsoft-trocr-small-printed & 1.392 & 0.150 & 7133 \\
% microsoft-trocr-base-printed & 1.286 & 0.081 & 3594 \\
microsoft-trocr-small-handwritten & \textbf{1.346} & 0.100  & 3947 \\
microsoft-trocr-base-handwritten & 1.549 & \textbf{0.057} & \textbf{3003} \\
\hline
\end{tabular}
\label{tab:text_digitization}
\end{table}

Some examples of the different models applied to our flowchart diagram dataset can be seen in Figure~\ref{fig:text_digitization_results_1} and in Figure~\ref{fig:text_digitization_results_2}.
